---
title: "How Weedios is being portrayed on YouTube 2016-2020"
fontsize: 18pt
output:
  html_document:
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
  pdf_document:  
    toc: yes
    toc_depth: 3
font-family: Arial
theme: united
---


<style>
  
#TOC {
 position: fixed;
  left: 0;
  top: 0;
  width: 250px;
  height: 100%;
  overflow:auto;
}
body {
  max-width: 1200px;
  margin: auto;
  margin-left:150px;
  line-height: 20px;
}
h1.title {
    font-size: 28px;
}
h4 {
    font-size: 20px;
}
h3 {
    font-size: 24px;
}
h2 {
    font-size: 25px;
}
h1 {
    font-size: 26px;
}
.center {
    display: block;
    margin-left: auto;
    margin-right: auto;
    width: 28%;
}
.table {
    width: 40%;
}

.btn {
    border-width: 0 0px 0px 0px;
    font-weight: normal;
    text-transform: ;
}
.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}
</style>

<hr>
<br>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
youtube <- read.csv("/Users/s4626133/Dropbox/1_PhD/2_Youtube analysis/04_final analysis/01_CleanedDataset_05052020.csv")
youtube1<-youtube
density1 <- read.csv("/Users/s4626133/Dropbox/1_PhD/2_Youtube analysis/04_final analysis/01_Density_05052020.csv")
#https://www.datasciencecentral.com/profiles/blogs/find-out-what-celebrities-tweet-about-the-most-1
```

```{r libraries, echo = FALSE, warning = FALSE, include = FALSE}
library(ggplot2)
library(DT)
library(dplyr)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(hrbrthemes)
library(ggridges)
library(viridis)
library(car)
library(robustbase)
```

# Dataset
```{r datavie, echo=FALSE}
datatable(youtube1)
```

<br>

# Advertisement
<hr>
<br>

```{r advert, echo=FALSE}
youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  count(advertisement) %>%
  filter(advertisement==1)

youtube1 %>%
  group_by(year) %>%
  count(advertisement) %>%
  filter(advertisement==1)
youtube1 %>%
  group_by(country) %>%
  count(advertisement) %>%
  filter(advertisement==1)
youtube1 %>%
  group_by(agerestrict) %>%
  count(advertisement) %>%
  filter(advertisement==1)
youtube1 %>%
  filter(advertisement==1) %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  filter(advertisement==1) %>%
  count(trying.products)
youtube1 %>%
  filter(advertisement==1) %>%
  summarise(median.views = median(as.numeric(views)), 
            min.views = min(as.numeric(views)), 
            max.views = max(as.numeric(views)), 
            iqr.views = IQR(as.numeric(views)), 
            q1.views = quantile(as.numeric(views), 0.25), 
            q3.views = quantile(as.numeric(views), 0.75),
            sum.views = sum(views),
            
            median.likes = median(as.numeric(likes)), 
            min.likes = min(as.numeric(likes)), 
            max.likes = max(as.numeric(likes)),
            q1.likes = quantile(as.numeric(likes), 0.25), 
            q3.likes = quantile(as.numeric(likes), 0.75), 
            
            median.dislikes = median(as.numeric(dislikes)), 
            min.dislikes = min(as.numeric(dislikes)), 
            max.dislikes = max(as.numeric(dislikes)), 
            iqr.dislikes = IQR(as.numeric(dislikes)),
            q1.dislikes = quantile(as.numeric(dislikes), 0.25), 
            q3.dislikes = quantile(as.numeric(dislikes), 0.75),
            
            median.comments = median(as.numeric(comments)), 
            min.comments = min(comments), 
            max.comments = max(comments))
 


```

# Product review
<hr>
<br>

```{r productreview, echo=FALSE}
youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  count(product.review) %>%
  filter(product.review==1)
youtube1 %>%
  group_by(year) %>%
  count(product.review) %>%
  filter(product.review==1)
youtube1 %>%
  group_by(country) %>%
  count(product.review) %>%
  filter(product.review==1)
youtube1 %>%
  group_by(agerestrict) %>%
  count(product.review) %>%
  filter(product.review==1)
youtube1 %>%
  filter(product.review==1) %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  filter(product.review==1) %>%
  count(trying.products)
youtube1 %>%
  filter(product.review==1) %>%
  summarise(median.views = median(as.numeric(views)), 
            min.views = min(as.numeric(views)), 
            max.views = max(as.numeric(views)), 
            iqr.views = IQR(as.numeric(views)), 
            q1.views = quantile(as.numeric(views), 0.25), 
            q3.views = quantile(as.numeric(views), 0.75),
            sum.views = sum(views),
            
            median.likes = median(as.numeric(likes)), 
            min.likes = min(as.numeric(likes)), 
            max.likes = max(as.numeric(likes)),
            q1.likes = quantile(as.numeric(likes), 0.25), 
            q3.likes = quantile(as.numeric(likes), 0.75), 
            
            median.dislikes = median(as.numeric(dislikes)), 
            min.dislikes = min(as.numeric(dislikes)), 
            max.dislikes = max(as.numeric(dislikes)), 
            iqr.dislikes = IQR(as.numeric(dislikes)),
            q1.dislikes = quantile(as.numeric(dislikes), 0.25), 
            q3.dislikes = quantile(as.numeric(dislikes), 0.75),
            
            median.comments = median(as.numeric(comments)), 
            min.comments = min(comments), 
            max.comments = max(comments),
            q1.comments = quantile(as.numeric(comments), 0.25), 
            q3.comments = quantile(as.numeric(comments), 0.75))
 

```

# Celebratory
<hr>
<br>

```{r celebrate, echo=FALSE}

youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  count(celebratory.video) %>%
  filter(celebratory.video==1)
youtube1 %>%
  group_by(year) %>%
  count(celebratory.video) %>%
  filter(celebratory.video==1)
youtube1 %>%
  group_by(country) %>%
  count(celebratory.video) %>%
  filter(celebratory.video==1)
youtube1 %>%
  group_by(agerestrict) %>%
  count(celebratory.video) %>%
  filter(celebratory.video==1)
youtube1 %>%
  filter(celebratory.video==1) %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  filter(celebratory.video==1) %>%
  count(trying.products)
youtube1 %>%
  filter(celebratory.video==1) %>%
 summarise(median.views = median(as.numeric(views)), 
            min.views = min(as.numeric(views)), 
            max.views = max(as.numeric(views)), 
            iqr.views = IQR(as.numeric(views)), 
            q1.views = quantile(as.numeric(views), 0.25), 
            q3.views = quantile(as.numeric(views), 0.75),
            sum.views = sum(views),
            
            median.likes = median(as.numeric(likes)), 
            min.likes = min(as.numeric(likes)), 
            max.likes = max(as.numeric(likes)),
            q1.likes = quantile(as.numeric(likes), 0.25), 
            q3.likes = quantile(as.numeric(likes), 0.75), 
            
            median.dislikes = median(as.numeric(dislikes)), 
            min.dislikes = min(as.numeric(dislikes)), 
            max.dislikes = max(as.numeric(dislikes)), 
            iqr.dislikes = IQR(as.numeric(dislikes)),
            q1.dislikes = quantile(as.numeric(dislikes), 0.25), 
            q3.dislikes = quantile(as.numeric(dislikes), 0.75),
            
            median.comments = median(as.numeric(comments)), 
            min.comments = min(comments), 
            max.comments = max(comments))
 
 

```


# Reflective
<hr>
<br>

```{r reflective, echo=FALSE}

youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  count(reflective) %>%
  filter(reflective==1)
youtube1 %>%
  group_by(year) %>%
  count(reflective) %>%
  filter(reflective==1)
youtube1 %>%
  group_by(country) %>%
  count(reflective) %>%
  filter(reflective==1)
youtube1 %>%
  group_by(agerestrict) %>%
  count(reflective) %>%
  filter(reflective==1)
youtube1 %>%
  filter(reflective==1) %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  filter(reflective==1) %>%
  count(trying.products)
youtube1 %>%
  filter(reflective==1) %>%
 summarise(median.views = median(as.numeric(views)), 
            min.views = min(as.numeric(views)), 
            max.views = max(as.numeric(views)), 
            iqr.views = IQR(as.numeric(views)), 
            q1.views = quantile(as.numeric(views), 0.25), 
            q3.views = quantile(as.numeric(views), 0.75),
            sum.views = sum(views),
            
            median.likes = median(as.numeric(likes)), 
            min.likes = min(as.numeric(likes)), 
            max.likes = max(as.numeric(likes)),
            q1.likes = quantile(as.numeric(likes), 0.25), 
            q3.likes = quantile(as.numeric(likes), 0.75), 
            
            median.dislikes = median(as.numeric(dislikes)), 
            min.dislikes = min(as.numeric(dislikes)), 
            max.dislikes = max(as.numeric(dislikes)), 
            iqr.dislikes = IQR(as.numeric(dislikes)),
            q1.dislikes = quantile(as.numeric(dislikes), 0.25), 
            q3.dislikes = quantile(as.numeric(dislikes), 0.75),
            
            median.comments = median(as.numeric(comments)), 
            min.comments = min(comments), 
            max.comments = max(comments))
 
```
 
 


# EVALI
<hr>
<br>


```{r evali, echo=FALSE}

youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  count(EVALI) %>%
  filter(EVALI==1)
youtube1 %>%
  group_by(year) %>%
  count(EVALI) %>%
  filter(EVALI==1)
youtube1 %>%
  group_by(agerestrict) %>%
  count(EVALI) %>%
  filter(EVALI==1)
youtube1 %>%
  filter(EVALI==1) %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  filter(EVALI==1) %>%
  count(trying.products)
youtube1 %>%
  filter(EVALI==1) %>%
  summarise(mean.views=mean(as.numeric(views)), mean.likes = mean(as.numeric(likes)), mean.dislikes = mean(as.numeric(dislikes)), mean.comments = mean(as.numeric(comments)) )
```

<br>
<br>

# How to
<hr>
<br>


```{r how.to, echo=FALSE}

youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  count(how.to) %>%
  filter(how.to==1)
youtube1 %>%
  group_by(year) %>%
  count(how.to) %>%
  filter(how.to==1)
youtube1 %>%
  group_by(country) %>%
  count(how.to) %>%
  filter(how.to==1)
youtube1 %>%
  group_by(agerestrict) %>%
  count(how.to) %>%
  filter(how.to==1)
youtube1 %>%
  filter(how.to==1) %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  filter(how.to==1) %>%
  count(trying.products)
youtube1 %>%
  filter(how.to==1) %>%
summarise(median.views = median(as.numeric(views)), 
            min.views = min(as.numeric(views)), 
            max.views = max(as.numeric(views)), 
            iqr.views = IQR(as.numeric(views)), 
            q1.views = quantile(as.numeric(views), 0.25), 
            q3.views = quantile(as.numeric(views), 0.75),
            sum.views = sum(views),
            
            median.likes = median(as.numeric(likes)), 
            min.likes = min(as.numeric(likes)), 
            max.likes = max(as.numeric(likes)),
            q1.likes = quantile(as.numeric(likes), 0.25), 
            q3.likes = quantile(as.numeric(likes), 0.75), 
            
            median.dislikes = median(as.numeric(dislikes)), 
            min.dislikes = min(as.numeric(dislikes)), 
            max.dislikes = max(as.numeric(dislikes)), 
            iqr.dislikes = IQR(as.numeric(dislikes)),
            q1.dislikes = quantile(as.numeric(dislikes), 0.25), 
            q3.dislikes = quantile(as.numeric(dislikes), 0.75),
            
            median.comments = median(as.numeric(comments)), 
            min.comments = min(comments), 
            max.comments = max(comments),
            q1.comments = quantile(as.numeric(comments), 0.25), 
            q3.comments = quantile(as.numeric(comments), 0.75))
 
```

<br>
<br>

# Cautionary video
<hr>
<br>

```{r cautionary.video, echo=FALSE}

youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  count(cautionary.video) %>%
  filter(cautionary.video==1)
youtube1 %>%
  group_by(year) %>%
  count(cautionary.video) %>%
  filter(cautionary.video==1)
youtube1 %>%
  group_by(country) %>%
  count(cautionary.video) %>%
  filter(cautionary.video==1)
youtube1 %>%
  group_by(agerestrict) %>%
  count(cautionary.video) %>%
  filter(cautionary.video==1)
youtube1 %>%
  filter(cautionary.video==1) %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  filter(cautionary.video==1) %>%
  count(trying.products)
youtube1 %>%
  filter(cautionary.video==1) %>%
   summarise(median.views = median(as.numeric(views)), 
            min.views = min(as.numeric(views)), 
            max.views = max(as.numeric(views)), 
            sum.views = sum(views),
            
            median.likes = median(as.numeric(likes)), 
            min.likes = min(as.numeric(likes)), 
            max.likes = max(as.numeric(likes)), 
            
            median.dislikes = median(as.numeric(dislikes)), 
            min.dislikes = min(as.numeric(dislikes)), 
            max.dislikes = max(as.numeric(dislikes)), 
            
            median.comments = median(as.numeric(comments)), 
            min.comments = min(as.numeric(comments)), 
            max.comments = max(as.numeric(comments)))
```

<br>
<br>


# Total videos
<hr>
<br>

```{r total.video, echo=FALSE}
youtube1 %>%
  group_by(year) %>%
  tally()
youtube1 %>%
  group_by(country) %>%
  tally()
youtube1 %>%
  group_by(agerestrict) %>%
  tally()
youtube1 %>%
  mutate( min = as.numeric(videolength_mins)) %>%
  mutate(sec = as.numeric(videolength_secs)) %>%
  mutate(length = min*60+sec) %>%
  summarize(mean.length.mins = mean(length)/60) 
youtube1 %>%
  count(trying.products)
youtube1 %>%
   summarise(median.views = median(as.numeric(views)), 
            min.views = min(as.numeric(views)), 
            max.views = max(as.numeric(views)), 
            iqr.views = IQR(as.numeric(views)), 
            q1.views = quantile(as.numeric(views), 0.25), 
            q3.views = quantile(as.numeric(views), 0.75),
            sum.views = sum(views),
            
            median.likes = median(as.numeric(likes)), 
            min.likes = min(as.numeric(likes)), 
            max.likes = max(as.numeric(likes)),
            q1.likes = quantile(as.numeric(likes), 0.25), 
            q3.likes = quantile(as.numeric(likes), 0.75), 
            
            median.dislikes = median(as.numeric(dislikes)), 
            min.dislikes = min(as.numeric(dislikes)), 
            max.dislikes = max(as.numeric(dislikes)), 
            iqr.dislikes = IQR(as.numeric(dislikes)),
            q1.dislikes = quantile(as.numeric(dislikes), 0.25), 
            q3.dislikes = quantile(as.numeric(dislikes), 0.75),
            
            median.comments = median(as.numeric(comments)), 
            min.comments = min(comments), 
            max.comments = max(comments),
            q1.comments = quantile(as.numeric(comments), 0.25), 
            q3.comments = quantile(as.numeric(comments), 0.75))
 
 
```

<br>
<br>


# Density rigeline plots
```{r density, ECHO = FALSE}
summary(density1$views)

density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(views), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, bandwidth = 15000, scale = 1.0)+
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Number of views") +
    ylab("Video themes")
  
density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(views), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, stat = "binline", bins = 50, scale = 0.9) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Number of views") +
    ylab("Video themes")
  
density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(likes), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, bandwidth = 50, scale = 1.0)+
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Number of likes") +
    ylab("Video themes")

density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(dislikes), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, bandwidth = 10, scale = 1.0)+
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Number of dislikes") +
    ylab("Video themes")

density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(comments), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, bandwidth = 10, scale = 1.0)+
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Number of comments") +
    ylab("Video themes")

density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(engagement), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, stat = "binline", bins = 50, scale = 0.9) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Engagement (num comments/num views)") +
    ylab("Video themes")


density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(popularity), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, stat = "binline", bins = 50, scale = 0.9) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Popularity (num views)") +
    ylab("Video themes")
  
density1 %>%
  filter(video.cat != "0") %>%
  ggplot(aes(x = as.numeric(positivity), y = video.cat, fill = video.cat)) +
  geom_density_ridges(alpha = 0.6, stat = "binline", bins = 50, scale = 0.9) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE)+ 
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )+
    xlab("Positivity (num likes/num views)") +
    ylab("Video themes")

```

 

# Correlates of number of views
<hr>
<br>


```{r regression, echo=FALSE}
youtube3 <- subset(youtube, select = c("views",  "likes", "dislikes","engagement", "positivity","popularity", "advertisement", "product.review", "celebratory.video","reflective","how.to", "cautionary.video", "time.since.upload", "comments", "engagement_type", "popularity_type", "positivity_type" ))

summary(youtube3)
youtube3$positivity<- as.numeric(youtube3$positivity)
youtube3$engagement<- as.numeric(youtube3$engagement)
youtube3$likes<- as.numeric(youtube3$likes)
youtube3$views<- as.numeric(youtube3$views)
youtube3$engagement_type <- factor(youtube3$engagement_type)



```

<br>
<br>


# Engagements
<hr>
<br>
```{r engagement, echo = FALSE}
a5.mod <-lmrob(engagement~  advertisement , data = youtube3)
summary(a5.mod)

a.mod <-lm(log(engagement+0.00001)~  advertisement , data = youtube3)
summary(a.mod)

mylogit <- glm(engagement_type~advertisement, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(engagement~ product.review, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(engagement+0.00001)~ product.review , data = youtube3)
summary(a.mod)

mylogit <- glm(engagement_type~product.review, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

a5.mod <-lmrob(engagement~ celebratory.video, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(engagement+0.00001)~ celebratory.video , data = youtube3)
summary(a.mod)

mylogit <- glm(engagement_type~celebratory.video, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(engagement~ reflective, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(engagement+0.00001)~ reflective, data = youtube3)
summary(a.mod)

mylogit <- glm(engagement_type~reflective, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(engagement~ how.to, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(engagement+0.00001)~ how.to, data = youtube3)
summary(a.mod)

mylogit <- glm(engagement_type~how.to, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

a5.mod <-lmrob(engagement~ cautionary.video, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(engagement+0.00001)~ cautionary.video, data = youtube3)
summary(a.mod)

mylogit <- glm(engagement_type~cautionary.video, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

mylogit <- glm(engagement_type~advertisement + product.review +celebratory.video+reflective+how.to+cautionary.video+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

<br>
<br>

# Popularity
<hr>
<br>
```{r popularity, echo = FALSE}
a1<-lmrob.control()
a1$maxit.scale<-3000

a5.mod <-lmrob(popularity~  advertisement +time.since.upload , control = a1, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(popularity)~  advertisement +time.since.upload, data = youtube3)
summary(a.mod)

mylogit <- glm(popularity_type~advertisement+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(popularity~ product.review+time.since.upload, control = a1, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(popularity)~ product.review +time.since.upload, data = youtube3)
summary(a.mod)

mylogit <- glm(popularity_type~product.review+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

a5.mod <-lmrob(popularity~ celebratory.video+time.since.upload, setting="KS2014",data = youtube3)
summary(a5.mod)

a.mod <-lm(log(popularity)~ celebratory.video +time.since.upload, data = youtube3)
summary(a.mod)

mylogit <- glm(popularity_type~celebratory.video+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(popularity~ reflective+time.since.upload, control = a1,data = youtube3)
summary(a5.mod)

a.mod <-lm(log(popularity)~ reflective+time.since.upload, data = youtube3)
summary(a.mod)

mylogit <- glm(popularity_type~reflective+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(popularity~ how.to+time.since.upload, setting="KS2014",data = youtube3)
summary(a5.mod)

a.mod <-lm(log(popularity)~ how.to+time.since.upload, data = youtube3)
summary(a.mod)

mylogit <- glm(popularity_type~how.to+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

a5.mod <-lmrob(popularity~ cautionary.video+time.since.upload, control = a1,  data = youtube3)
summary(a5.mod)

a.mod <-lm(log(popularity)~ cautionary.video+time.since.upload, data = youtube3)
summary(a.mod)

mylogit <- glm(popularity_type~cautionary.video+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

mylogit <- glm(popularity_type~advertisement + product.review +celebratory.video+reflective+how.to+cautionary.video+time.since.upload, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

```

<br>
<br>

# Positivity
<hr>
<br>
```{r positivity, echo = FALSE}
a5.mod <-lmrob(positivity~  advertisement , data = youtube3)
summary(a5.mod)

a.mod <-lm(log(positivity+0.00001)~  advertisement , data = youtube3)
summary(a.mod)

mylogit <- glm(positivity_type~advertisement, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(positivity~ product.review, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(positivity+0.00001)~ product.review , data = youtube3)
summary(a.mod)

mylogit <- glm(positivity_type~product.review, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

a5.mod <-lmrob(positivity~ celebratory.video, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(positivity+0.00001)~ celebratory.video , data = youtube3)
summary(a.mod)

mylogit <- glm(positivity_type~celebratory.video, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(positivity~ reflective, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(positivity+0.00001)~ reflective, data = youtube3)
summary(a.mod)

mylogit <- glm(positivity_type~reflective, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))


a5.mod <-lmrob(positivity~ how.to, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(positivity+0.00001)~ how.to, data = youtube3)
summary(a.mod)

mylogit <- glm(positivity_type~how.to, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

a5.mod <-lmrob(positivity~ cautionary.video, data = youtube3)
summary(a5.mod)

a.mod <-lm(log(positivity+0.00001)~ cautionary.video, data = youtube3)
summary(a.mod)

mylogit <- glm(positivity_type~cautionary.video, data = youtube3, family = "binomial")
summary(mylogit)
exp(cbind(OR = coef(mylogit), confint(mylogit)))

```


